---
title: "GPU_heat"
author: "Callum Simpson"
date: "30/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
```

```{r include=FALSE}
# Load project
source("src/GPU_heat_code.R")
```

This report will be looking into how certian factors effect the GPU heat.

High temperature will have two negative effects on a GPU.

- A high temperatures will shorten the life of hardware. Partically damaged GPU may increase the GPU processing time due , slowing down the processes. Fully damaged GPU would need to be replaced adding in a additional cost to the processes. There is also the potential that too hot of a temperature could cause more damage to the host than just damaging the GPU, taking down the whole machine.
- GPU typically have a fail safe that will try and combat high temperature by ether slowing down in order to cool down or fully shut down. Both would increase the time needed to run a programme.

So we need to investigate what effect using cloud computers to make Terapixel has an effect on a GPU and if they are being pushed to the point at which they may be damaged.

## Memory utlisation and tempreture 

Before I looked into how temperature was effected by performance I went about looking into whether an increase in memory utilization had an effect on GPU temperature.

We see that there is as Memory utilization increases it changes the temperature in some weird ways. 

At low utilization zero (so not running) temprature as its lowest of 37. we then see as utlisation slightly increases we see a a jump to around 40 degrees. We then notice 3 trends
- betweeb 5% and 35% the temparture stays at around 40 degrees. 
- There is then a sudden jump to around 41 degrees up until 60 percent
- Between memory utlisation 60% to 80% we see that temprature slowly starts to decrease to around 38 degrees. 

```{r heat_util_gpuMemUtilPerc}
ggplot(heat_util_gpuMemUtilPerc, aes(gpuMemUtilPerc,median)) + geom_line()  + geom_point() + geom_errorbar(aes(ymin=qt1, ymax=qt3), width=0.25)
```

## GPU utlisation and tempreture 

I also wanted to see how GPU utilization effected temperature.

We see that there is a slow increase in temperature as GPU utilization increases.  

```{r heat_util_gpuMemUtilPerc}
ggplot(heat_util_gpuUtilPerc, aes(gpuUtilPerc,median)) + geom_line()  + geom_point() + geom_errorbar(aes(ymin=qt1, ymax=qt3), width=0.25)
```

## GPU performance

One statistic that can be used to calculated the performance of a GPU is fill rate, the number of pixels that can be rendered by the card per second.

