---
title: "render_map"
author: "Callum Simpson"
output:
  pdf_document: default
  word_document: default
  html_document:
  df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))

options(digits=2)
```


```{r include=FALSE}
# Load project
library('ProjectTemplate')
load.project()

source('src/Events_Explore_code.R')

```

This is my report of my CSC8634: Cloud computing with Project.

In this report I will be discussing how I under took a Performance evaluation project on a set of data  relating to the creation of a Terapixel rendering in Cloud (Super)computing.

## A background 

A Terapixel image offers a new and intuitive way to present information sets to stakeholders that is also extremely accessible to all, allowing viewers to interactively browse big data across multiple scales. Typically made up of over one trillion pixels and provide a fluid experience where the viewer can see an overview of the whole image or zoom into incredible detail. 

The importance of Terapixel images is that viewing it only depends on the image display capabilities of the web browser that can display it, making terapixel images accessible on a wide range of thin clients. The client would not need any expensive software or hardware to view the image, only a web browser and a link. Terrapixels can also be very detailed allowing for impressive designs that a client might require.

This project will be a performance evaluation looking at processes behind creating the first terapixel visualization of IoT data within a 3D urban environment by Members of Newcastle university.

Petascale Cloud Super computing for Terapixel Visualization of a Digital Twin (https://arxiv.org/ftp/arxiv/papers/1902/1902.04820.pdf) 

The image created to was a realistic 3D visualization of the city of Newcastle upon Tyne to display psychical locations of a set of sensors that are located around the university. One of the big parts of this project was that it was created by using a scalable architecture for cloud-based visualization meaning the user 
can control what they deploy and pay for.

The project had three key goals to achieve this

- create a supercomputer architecture for scalable visualization using the public cloud
- produce a terapixel 3D city visualization supporting daily updates 
- undertake a rigorous evaluation of cloud supercomputing for compute intensive visualization applications.

In this project the Terapixel visualization using a path tracing renderer the image in under an hour using 1024 public IaaS cloud GPU nodes.

https://arxiv.org/ftp/arxiv/papers/1902/1902.04820.pdf

## What is the reasons for this project

The aim of this project is to undertake a Performance evaluation of data collected about the creation of this TeraPixel image using cloud computing to find areas in which we could improve.

There are two areas we can foucs on in this project to help improve the creation of Terapixel projects in the future. 

Firstly We know that Terapixel is held back time and power costs so we would want to ivestergate how the we could reduce both these things

As we have the data about the clouds 1024 nodes that where used to create this image then work should be performed an analysis on this sector to see if we could find any issue that should be fixed/ improved for future runs.


## What I did and discovered


## The success of my project


## Future implications for work from this project 


## Reflection